Disease and climate effects on individuals jointly drive post-reintroduction

### 2018-05-27 article.Rmd
citing GitHub repo

All code and data necessary to reproduce the analysis and manuscript is publicly available at [https://www.github.com/snarl1/sierra-reintroduction-cmr](https://www.github.com/snarl1/sierra-reintroduction-cmr). 
The workflow is wrapped into GNU Make command [@Stallman2004], the manuscript is written in R Markdown [@rmarkdown], and we used the R programming language [@r-lang] with the assertthat, ggrepel, ggridges, ggthemes, lubridate, mgcv, patchwork, reshape2, rstan, and tidyverse packages to facilitate data processing, model fitting, and visualization [@assertthat; @ggrepel; @ggridges; @ggthemes; @lubridate; @mgcv; @patchwork; @reshape2; @rstan; @tidyverse].
The computational environment with these dependencies is containerized via Docker, and the Dockerfile for the image exists in the GitHub repository for this project [@boettiger2015introduction].

>>>>

All code and data necessary to reproduce the analysis and manuscript is publicly available at [https://www.github.com/snarl1/sierra-reintroduction-cmr](https://www.github.com/snarl1/sierra-reintroduction-cmr) [@joseph_2018]. 
The workflow is wrapped into GNU Make command [@Stallman2004], the manuscript is written in R Markdown [@rmarkdown], and we used the R programming language [@r-lang] with the assertthat, ggrepel, ggridges, ggthemes, lubridate, mgcv, patchwork, reshape2, rstan, and tidyverse packages to facilitate data processing, model fitting, and visualization [@assertthat; @ggrepel; @ggridges; @ggthemes; @lubridate; @mgcv; @patchwork; @reshape2; @rstan; @tidyverse].
The computational environment with these dependencies is containerized via Docker, and the Dockerfile for the image exists in the GitHub repository for this project [@boettiger2015introduction].
